On the properties of discs around accreting brown dwarfs

### 2010-06-30 BDD_submit/paper.tex
More adjustment to figure caption number 7
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2333 25464f21-6099-402c-b30a-640f1d40d38b

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
    inclination, shown as top, middle and lower panels
    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
    days are shown as solid lines. The systems with accretion rates of
    \logmdot = $-$12, $-$9 and $-$7, are shown in black, red and blue
    respectively. The panels also show the systems with the highest
    accretion rate but for a rotation rate of 5 days, as a dashed
    line. The vertical dotted lines show the inclinations of
    71$^{\circ}$ and 56$^{\circ}$. Finally, the inset panel simply
    shows a magnification of the region of interested for the $M_J$
    magnitude. \label{flare_mag}}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/flare_mag.ps}
  \caption{Figure showing $M_V$ and $M_J$ magnitudes as a function of
    inclination, shown as top, middle and lower panels
    respectively. The magnitudes of systems with $M_*=0.04M_{\odot}$,
    an age of 1 Myr, areal coverage of 10\% and rotation rate of 0.5
    days are shown as solid lines (and crosses). The systems with
    accretion rates of \logmdot = $-$12, $-$9 and $-$7, are shown in
    black, red and blue respectively. The panels also show the systems
    with the highest accretion rate but for a rotation rate of 5 days,
    as dashed lines (and crosses). The vertical dotted lines show the
    inclinations of 71$^{\circ}$ and 56$^{\circ}$. Finally, the inset
    panel simply shows a magnification of the region of interested for
    the $M_J$ magnitude. \label{flare_mag}}
\end{figure*}
